HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-15 LaTeX/ms.tex
Added units to Table 5

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~Scudders\altaffilmark{3},
C.~Hayward\altaffilmark{4,5},
W.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
Hai~Fu\altaffilmark{11},
R.~Gavazzi\altaffilmark{12},
R.~Hopwood\altaffilmark{13},
R.~J.~Ivison\altaffilmark{14,15},
M.~Jarvis\altaffilmark{16},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{17,18},
D.~Rigopoulou\altaffilmark{19,20},
I.~G.~Roseboom\altaffilmark{3,15},
Douglas~Scott\altaffilmark{21},
A.~J.~Smith\altaffilmark{3},
L.~Wang\altaffilmark{3},
J.~Wardlow\altaffilmark{22}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{12}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{13}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{14}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{15}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{17}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{18}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{19}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{20}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{21}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{22}{Dark Cosmology Centre, Niels Bohr Institute, University of
Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

>>>>

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~Scudders\altaffilmark{3},
C.~Hayward\altaffilmark{4,5},
W.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
Hai~Fu\altaffilmark{11},
R.~Gavazzi\altaffilmark{12},
R.~Hopwood\altaffilmark{13},
R.~J.~Ivison\altaffilmark{14,15},
M.~Jarvis\altaffilmark{16},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{17,18},
D.~Rigopoulou\altaffilmark{19,20},
I.~G.~Roseboom\altaffilmark{3,15},
Douglas~Scott\altaffilmark{21},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{7},
L.~Wang\altaffilmark{3},
J.~Wardlow\altaffilmark{22}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{12}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{13}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{14}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{15}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{17}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{18}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{19}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{20}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{21}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{22}{Dark Cosmology Centre, Niels Bohr Institute, University of
Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}
